TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2019-07-13 paper/draft.tex
ref catalog table
notes to self
more discussion

% \color{gcolor}{BIRKY: Can you demonstrate this by showing the RMS residuals, putting it in as a figure, and putting this paragraph back to me? I am imagining a figure that shows a scatter plot of T vs RMS residual, colored by metallicity. Or something like that.}\color{black} \\

% \color{gcolor}{HOGG: Adam's comment: if $\chi^2/n>>1$ then the model is NOT an accurate representation of the data.}\color{black} \\

@@

Table \ref{table:test_results} presents...

@@

Talk about the particular limitations we have found in this training sample. Talk about model improvements: incorporate broadening \citep{Behmard2019}; spectroscopic binary model \citep{ElBadry:2018}... \\

@@

Talk future work/implications with other stellar surveys (e.g. LAMOST), and exoplanet surveys (e.g. TESS)

>>>>

@@

Table \ref{table:test_results} outlines the parameters included in the test sample catalog, which can be downloaded from the online journal.

@@

The model we have developed does have limitations however.
For example, it delivers chi-squared values---goodness-of-fit measures---that
are large; the model is not technically an accurate description of the spectra,
especially when the spectra are observed at signal-to-noise levels above 100.
For another, it does not include some known physical and instrumental effects.
It does not include a term or terms for line broadening from rotation or
convection (\eg, \citealt{Behmard2019}).
It does not include any accounting for binarity or superposition of multiple
stellar spectra (as in, say, \citealt{ElBadry:2010}).
And it does not include any adjustments for instrumental variations, like for
example the small but significant variations of \apogee\ resolution with
spectrograph fiber number (as are included in \citealt{Ness2018}).

In addition to all this, the \apogee\ instrument was designed to be sensitive to more than
a dozen individual element abundances in stellar spectra!
So the M-dwarf spectra analyzed here contain individual element abundance
information that we have left on the table.
Exploitation of that information might require better models of M dwarfs than
we have at present.
However, this is an important goal for the future with these data.

@@

HOGG: Talk future work/implications with other stellar surveys (e.g. LAMOST), and exoplanet surveys (e.g. TESS)
